\chapter{Hardware and Software}
\label{hardwareandsoftware}

This chapter will give an in-depth look into the hardware and software used to complete the project. This knowledge is necessary to understand the design decisions made.

\section{Hardware}

\subsection{Rotary Encoder}
A rotary encoder is an electromechanical transducer to convert a rotary movement into a electrical signal. One of the most commonly used rotary encoders is the optical rotary encoder.
Its working principle is based on a Light emitting diode and a photo sensitive device, such as a photo-transistor or photo-resistor. The diode and the photo-sensitive device are located on opposite sides of a light blocking disk. 
The light blocking disk is is perforated with small slits in a rotations symmetric and regular pattern. As soon as the disc is rotated between the diode and the photo-sensitive device the light is transmitted and blocked in an alternating pattern.
This creates a squarewave on the output of the photo-sensitive device which frequency is dependant on the rotationary speed of the disk.

%%TODO Bild??
%%TODO Quelle???

\subsection{Stepper Motors}
A stepper motor is an electrical, synchronous motor. Its rotor follows the magnetic field created in the stator exactly. In contrast to commonly known DC or AC motors, a stepper motor has a minimum angle that it needs to be rotated. 
This has the big advantage, that the position is always a multiple of the step angle. Therefor a sensor is not necessary to rotate the motor by a very precise amount. A stepper motor is a cheap alternative to 
closed loop controlled motors, where an additional sensor has to determine the positional error of the motor in order to move the motor precisely.\\
The disadvantage of stepper motors usually is their low rpm limit. At a certain speed, the rotor of the motor is no longer able to follow the magnetic field created by the stator. 
This can also happen when the motor is under high load and is very hard to detect. Therefore, stepper motors are often combined with rotational sensors in order to compensate the positional error, when the motor comes out of synchronization.\cite{SchrittmotorenFaulhaber2022}

\subsection{Closed Loop Servos}
Closed Loop Servos is an electromechanical actuator with an continuous feedback loop between its output (speed, torque, position, etc..) and input. 
Servos require additional electronics to compute the difference between its desired output of the motor and its current output. These electronics are usually referred to as "controller" or "driver".
Servos are used in a wide variety of mechatronic applications when high precision, reliability or dynamics are required.\cite{ServoSuh2008}

\subsection{Microcontroller}
A Mikrocontroller is an integrated circuit designed to serve a specific task in a system. Mikrocontroller consist of a processing unit, memory and In- and Outputs. 
Within the system Mikrocontrollers can be used for a wide variety of tasks such as communication, data acquisition or motor control. For mechatronic tasks, microcontrollers are commonly used in an so called embedded system. 
An embedded system is usually designed around a microcontroller and a specific task within a project.\cite{UensalanMicrocont2022}

\subsubsection{TI LaunchXL F280049C}
The Texas Instruments Launchpad F280049C is a prototyping board designed around their Picolo F280049C Real-Time microcontroller as an embedded system. Its design specificallay targets highly dynamic controll tasks while maintaining a low unit cost.
The Picolo F280049C is a 32bit floating point microcontroller with 256KB Flash memory, 100KB RAM and a operation frequency of 100MHz. 
Further, the microcontroller has hardware support for up to two rotary encoder, a wide variety of communication protocolls and general purpose I/O. 
In addition, the LaunchPad developement board build around the microcontroller offers a debugging probe. This probe can be used to flash the microcontroller with maschinecode or observe and direct the operation of the microcontroller. 
This way it is for excample possible to stop the execution of the program on the microcontroller and access the value of every bit in every register of the microcontroller.\cite{TILAUNCHXL}

\subsubsection{Logic Level Shifter}
A logic level shifter is an electronic circuit designed to convert one logic voltage level into another one, while maintaining the signal integrity. In modern mechatronic systems it is often necessary 
that different electronic systems can communicate with each other. In some cases however, it is not possible that all components work with the same voltage level. This makes it inevitable to use a logic level shifting circuit.

%%TODO Quelle???

\subsection{Raspberry Pi}
A Raspberry Pi is a Single board computer that features a full graphic operating system based on linux. Further it offers wireless conectivety as well as general purpose I/O's. The raspberry pi is mostly open source and very cost effective.
Because it has a very wide customer base, the Raspberry Pi has wide variety of hardware and software add-ons available.\cite{RaspberryPiFoundation}
%%TODO Bild??
%%TODO Quelle???

\subsubsection{Touchscreen}
A touchscreen is a Human Maschine Interface (HMI) that can display information and react to touch inputs. The commonly used touchscreen combines a regular LED screen with touch sensitive layer. 
Highly sensitive touchscreens that can detect multiple touch inputs at once, usually work on a capacitive principle. 
%%TODO Bild??
%%TODO Quelle???

\section{Software}
\subsection{Matlab and Matlab-Simulink}
MATrix LABoratory (MATLAB) is an Integrated Development Environment (IDE)
and programming language. MATLAB was developed in the need of a numerical algebraic
system at the university of New Mexico. On this base, the company MathWorks (see
\ref{AppendixListOfCompanies}) was created. Since 1984 MathWorks is further developing MATLAB and
additional software for numerical algebraic computing. To support different hardware
packages MathWorks offers so called toolboxes. These toolboxes contain functions and
scripts for communication, data acquisition, motion control etc.
MATLAB is mainly used in technical development and research.\cite{Mathworks}

\subsection{Programing Language C}
C is a high level programing language. It is most commonly used to write applications for embedded systems. It is chosen over low level programing languages 
such as Assembly because of the increasing complexity of programs for embedded systems. C is a compiled programming language. This means that a program needs to be translated (compiled) to machine code before it can be executed. 
This translation is done with a program called "compiler". Compared to lower level languages such as Assembly, the code reusability of C has proven to be a step forward in the development of embedded systems.\cite{ISO2022}


\subsection{Programing Language Python}
Python is a high level object oriented programming language. In contrast to C, Python is an interpreted language. This means, an Interpreter translates source code into machine commands in 
real time, while the program is executed. Python features a good combination of capability and ease of uses. This makes the language easy to learn for beginners while remaining very powerful.
Python further features a huge variety of proprietary and community build support packages and is based on the one of the most used programming languages used today.\cite{PythonFoundation2022}

\subsubsection{Kivy}
Kivy is an open source Python library for the rapid development of grafical user interfaces and apps. 
It is script based and its scripting language can bei directly implemented in Python. Further, kivy supports use with touch screens.\cite{Kivy.org2022}


\subsection{Code Composer Studio}
Code Composer Studio is an Integrated Development Environment produced by Texas Instruments. It presents an interface to the Hardware produced by Texas Instruments and offers optimizing compilers for C and C++. 
Further, Code Composer Studio features support packages for the development and deployment of software to Texas Instruments Hardware such as the TI LaunchXL F280049C.
These support packages in combination with a hardware debugging probe, enable the programmer To interact with the processor in real time.\cite{Instruments2022}


\subsection{Git}
Git is an software tool for source code management and versioning, as well as for parallel development. 
Git was developed by Linus Torvald in 2005. Git was developed in the need of source code management software for the development of the operating system Linux.
Git allows development in so-called branches. These are independent copies of an already existing and probably used software. 
This ensures that modifications or enhancements are not affecting already used software. If a feature is finished, it can be merged back into the higher-level branch. 
Merging is the process of bringing two files, directories or branches together.
Different developers, working on different features of the same project is called parallel development.
Further Git is a tool for software versioning. Software versioning is a tracking of changes in a project. 
In case of an mistake the project can be recovered to every tracked point.
Git was very heavily used for software development after and during our testing. 
%%TODO Quelle???
